
## Sleep study

- This is assignment 6 (partially) in week 7 as well as Assignment 8 #3 and #4 

```{r}
data(sleepstudy, package = "lme4")
library(brms)
```



## Random intercepts model

```{r}
( priorsRI <- c(
  prior(
    normal(250, 100),
    class = "b",
    coef = "Intercept"
  ),
  prior(
    normal(0, 20),
    class = "b",
    coef = "Days"
  ),
  prior(
    normal(0,100),
    class = sd,
    group = "Subject",
    coef = "Intercept"

  ),
  prior(
    normal(0, 100),
    class = "sigma"
  )


))

fit <- brms::brm(bf(Reaction ~ Days +  (1 | Subject),family = "gaussian", center=FALSE),
                 prior = priorsRI, data = sleepstudy)

```

we note that this gives for population level effect of days on reaction as 10.45 +- 0.79

## Random slopes version

```{r}
( priorsRS <- c(
  prior(
    normal(250, 100),
    class = "b",
    coef = "Intercept"
  ),
  prior(
    normal(0, 20),
    class = "b",
    coef = "Days"
  ),
  prior(
    normal(0,100),
    class = sd,
    group = "Subject",
    coef = "Intercept"

  ),
  prior(
      normal(0,20),
      class = 'sd',
      coef = 'Days',
      group = 'Subject'
  ),
  prior(
    normal(0, 100),
    class = "sigma"
  ),
  prior(
    lkj(2),
    class = "cor"
  )


))

modelf <- bf(Reaction ~ Days +  ( 1 + Days | Subject),family = "gaussian", center=FALSE)

fit2 <- brms::brm(modelf,
                  prior = priorsRS,
                   data = sleepstudy, save_pars = save_pars(all = TRUE))
```

For random slopes version , the estimated slope on Days was 10.42 +-1.72 .
Subject specific effect sd on days was 6.6

## Compare (Assignment 8, part 3)

- Look first at random intercepts posterior checks

```{r}
pp_check(fit)
```

Not terrible, not great :)

```{r}
pp_check(fit, type = "intervals_grouped", x = "Days", group = "Subject")
```
Doesn't appear that constant slope is 'great' here.

Lets look at varying slopes:
```{r}
pp_check(fit2)
```
Maybe slightly better??
```{r}
pp_check(fit2, type = "intervals_grouped", x = "Days", group = "Subject")
```

Varying slopes do look better here. Lets compare loo:

```{r}
fit <- add_criterion(fit,"loo")
fit2 <- add_criterion(fit2, "loo", moment_match=TRUE)
loo_compare(fit,fit2)
```

Not sure I am using the moment_match correctly. 

But there is a significant difference, fit2 is better. 


## Part 4 

- Reaction times are known to be positively skewed, so lets use log normal instead.  I dont want to refit a million models so i will stick with the varying slopes

```{r}

# priors are now in log space

( priorsRS <- c(
  prior(
    normal(log(250), 1),
    class = "b",
    coef = "Intercept"
  ),
  prior(
    normal(0, 1),
    class = "b",
    coef = "Days"
  ),
  prior(
    normal(0,1),
    class = sd,
    group = "Subject",
    coef = "Intercept"

  ),
  prior(
      normal(0,1),
      class = 'sd',
      coef = 'Days',
      group = 'Subject'
  ),
  prior(
    normal(0, 2),
    class = "sigma"
  ),
  prior(
    lkj(2),
    class = "cor"
  )


))

modelf <- bf(Reaction ~ Days +  ( 1 + Days | Subject),family = "lognormal", center=FALSE)

fit_lognormal <- brms::brm(modelf,
                  prior = priorsRS,
                   data = sleepstudy)
```

```{r}
pp_check(fit_lognormal)
```

ppcheck is better!


```{r}
 
fit_lognormal<- add_criterion(fit_lognormal, "loo")
loo_compare(fit,fit2, fit_lognormal)
```


The lognormal family does even better.

### Spline case

```{r}


( priorsSpline <- c(
  prior(
    normal(log(250), 1),
    class = "b",
    coef = "Intercept"
  ),
  prior(
    normal(0, 1),
    class = "b",
    coef = "Days"
  ),
  prior(
    normal(0,1),
    class = sd,
    group = "Subject",
    coef = "Intercept"

  ),
  prior(
      normal(0,1),
      class = 'sd',
      coef = 'Days',
      group = 'Subject'
  ),
  prior(
    normal(0, 2),
    class = "sigma"
  ),
  prior(
    lkj(2),
    class = "cor"
  ), 
  prior(
    normal(0,1),
    class = "b",
    coef = "sDays_1"
  )


))
modelf <- bf(Reaction ~ Days + s(Days) +  ( 1 + Days | Subject),family = "lognormal", center=FALSE)

fit_spline <- brms::brm(modelf,
                  prior = priorsSpline,
                   data = sleepstudy)
```


```{r}
pp_check(fit_spline)
```

```{r}
 
fit_spline <- add_criterion(fit_spline, "loo")
loo_compare(fit,fit2, fit_lognormal, fit_spline)
```

The spline fit is not significantly better, which makes sense as the spline coefficients are consistent with zero. However, one thing this assignment has taught me is that I dont really know much about GAM models .

```{r}
fit_spline
```

```{r}
pp_check(fit_spline, type = "intervals_grouped", x = "Days", group = "Subject")
```
